A Formal Model of Checked C

### 2022-07-15 sandp23/formal.tex
update.

        \inferrule[S-Let]{}{(\varphi,\heap,\elet{x}{\evalue{n}{\tau}}{e}) \longrightarrow (\varphi[x\mapsto \evalue{n}{\tau}],\heap,\ret{x}{\varphi(x)}{e})}

@@

\myparagraph{Binding and Function Calls}
%
The semantics handles variable scopes using the special $\erettext$
form. \textsc{S-Let} evaluates to a configuration whose stack
is $\varphi$ extended with a binding for $x$, and whose expression is
$\ret{x}{\varphi(x)}{e})$ which remembers $x$ was previously bound to
$\varphi(x)$; if it had no previous binding, $\varphi(x) =
\bot$. Evaluation proceeds on $e$ until it becomes a literal
$n\!:\!\tau$, in which case \textsc{S-Ret} restores the saved
binding (or $\bot$) in the new stack, and evaluates to
$n\!:\!\tau$.

>>>>

        \inferrule[S-Let]{}{(\varphi,\heap,\elet{x}{\evalue{n}{\tau}}{e}) \longrightarrow (\varphi,\heap,\ret{x}{\evalue{n}{\tau}}{e})}

@@

\myparagraph{Binding and Function Calls}
%
The semantics handles variable scopes using the special $\erettext$
form. \textsc{S-Let} evaluates to a configuration whose stack
is $\varphi$ extended with a binding for $x$, and whose expression is
$\ret{x}{\evalue{n}{\tau}}{e})$ which keeps $\varphi$ unchanged, but
remember $x$ with the new value $\evalue{n}{\tau}$ in the scope $e$.
Every time when Evaluation proceeds on $e$ (Rule \textsc{S-RetCon}),
we install the current stack value $\evalue{n}{\tau}$ for $x$ in $\varphi$,
after one-step evaluation is completed, we restore the result $\varphi'(x)$ 
in the result $\ret{x}{\varphi'(x)}{e'})$.
This procedure continues until it becomes a literal
$n\!:\!\tau$, in which case \textsc{S-RetEnd} remove the $\kw{ret}$ frame and evaluates to
$n\!:\!\tau$.
